Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-12 manuscript/climate_sensitivity_draft.Rmd
Updated manuscript

---
title: "Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Neil Pederson, Lawren Sack, Krista Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [book.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small} 
- \usepackage{dcolumn} #for sidewaystable
---

@@

@@

![Time series of combined tree cores by species](tables_figures/Time_series_for_each_species.jpg){width=500px}

@@

![Height profile graphs]
(tables_figures/height graphs ){width=500px}

@@

(see Issue #32)

**include TWI by trait graphs (2) here**

>>>>

---
title: "Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Neil Pederson, Lawren Sack, Krista Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [book.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

@@

![Location of cored trees](tables_figures/Figure3.png){width=500px}

@@

![Time series of combined tree cores by species](tables_figures/Figure1.jpg){width=500px}

@@

![Height profile graphs](tables_figures/Figure2.png){width=500px}

@@

![Figure S1](tables_figures/Table3.png) #this is tested_traits_all
(see Issue #32)
